Optimal (Multiway) Spatial Joins

### 2024-06-06 msj.tex
yufei

\extraspacing {\underline{\em Example 4.2.}} Figure~\ref{fig:hv:type1:ex}b shows the rectangles in $R'_1 = \set{\alpha'}$ and $R'_2$ $=$ $\{\beta'_1,$ $\beta'_2\}$. For instance, $\alpha'$, which is trimmed from rectangle $\alpha$, is decided by $h_\bot$ $=$ $h_2$, $h_\top$ $=$ $h_6$, $v_\vdash = v_3$, and $v_\dashv = v_5$. The $(k-2)$-SJ on $R'_1$ and $R'_2$ returns $\J(R_1', R'_2, ..., R'_{k-2}) = \set{(\alpha', \beta_1'), (\alpha', \beta_2')}$.
\done

@@

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $B_\bm{t}$ --- defined in \eqref{eqn:B_t} --- is the point $h' \cap v$ (the intersection of $h'$ and $v$). Suppose $h' = [x_1, x_2] \times y$ and $B_\bm{t} = (x, y)$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment $[x_1, x] \times y$. This allows us to define
\myeqn{
    \contain_{R_{k-2}}(\bm{t}) = \{r \in R_{k-2} \mid \text{$r$ contains the effective horizontal segment of $\bm{t}$}   \}
    \label{eqn:type2:contained-t}
}
The above should not be confused with \eqref{eqn:contained}, where the ``$\contain$'' function takes a segment as the parameter, rather than a tuple.

@@

\begin{lemma} \label{lmm:hv:type2:properties}
    All the following statements are true:
    \myenums{
        \item Consider any $(k-1)$-tuple $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$. Denote by $h$ the full segment of $\bm{t}[k-2]$. Then, for any $r \in \contain_{R_{k-2}}(\bm{t})$, the $k$-tuple $(\bm{t}[1], ..., \bm{t}[k-3], r, h, \bm{t}[k-1])$ must belong to $\J_2$.

>>>>

\extraspacing {\underline{\em Example 4.2.}} Figure~\ref{fig:hv:type1:ex}b shows the rectangles in $R'_1 = \set{\alpha'}$ and $R'_2$ $=$ $\{\beta'_1,$ $\beta'_2\}$. For instance, $\alpha'$, which is trimmed from rectangle $\alpha$, is decided by $h_\bot$ $=$ $h_2$, $h_\top$ $=$ $h_6$, $v_\vdash = v_3$, and $v_\dashv = v_5$. The $(k-2)$-SJ on $R'_1$ and $R'_2$ returns $\J(R_1', R'_2) = \set{(\alpha', \beta_1'), (\alpha', \beta_2')}$.
\done

@@

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $B_\bm{t}$ --- defined in \eqref{eqn:B_t} --- is the point $h' \cap v$ (the intersection of $h'$ and $v$). Suppose that $h' = [x_1, x_2] \times y$ and $B_\bm{t} = (x, y)$; we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment $[x_1, x] \times y$. This allows us to define
\myeqn{
    \contain_{R_{k-2}}(\bm{t}) = \{r \in R_{k-2} \mid \text{$r$ contains the effective horizontal segment of $\bm{t}$}   \}
    \label{eqn:type2:contained-t}
}
The above should not be confused with \eqref{eqn:contained}, where the ``$\contain$'' function takes a segment as the parameter, rather than a tuple.

@@

\begin{lemma} \label{lmm:hv:type2:properties}
    All the following statements are true:
    \myenums{
        \item Consider any $(k-1)$-tuple $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$. Denote by $h$ the full segment of $\bm{t}[k-2]$. Then, for any $r \in \contain_{R_{k-2}}(\bm{t})$, the $k$-tuple $(\bm{t}[1], ..., \bm{t}[k-3], r, h, \bm{t}[k-1])$ belongs to $\J_2$.
